Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-05-29 neurips-20/cvx-flats.tex
Moving calibration statements to the appendix.

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\simplex}{\Delta_\Y}
\newcommand{\relint}[1]{\mathrm{relint}(#1)}
\newcommand{\prop}[1]{\mathrm{prop}[#1]}
\newcommand{\elic}{\mathrm{elic}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
\newcommand{\ccdim}{\mathrm{ccdim}}
\newcommand{\codim}{\mathrm{codim}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\supp}{\mathrm{supp}}
\newcommand{\spn}{\mathrm{span}}
\newcommand{\propdis}{\mu}
\newcommand{\affhull}{\mathrm{affhull}}

@@

\subsection{Consistency and calibration for convex losses}\label{subsec:convex-surrogates}

@@

\cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} form a characterization of consistent and calibrated surrogates for classification problems.
In finite prediction tasks, the two are in fact equivalent.  
\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, there is a consistent surrogate for binary classification problems, and~\cite{tewari2007consistency} generalizes this result for multiclass classification. 
\cite{ramaswamy2016convex} further show necessary and sufficient conditions for finite prediction problems to be consistent that can be applied to general discrete losses.
\cite{steinwart2007compare} generalizes the study of consistent losses from the finite prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration, giving proofs for various classes of surrogate losses (i.e. margin-based, distance-based, supervised, unsupervised, etc.)
See~\cite[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
In Appendix~\ref{app:calibration}, we give a more general definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in finite outcome settings, but generalizes to infinite outcome settings.

@@

\paragraph{Our approach: indirect elicitation.}
In this section, we show that indirect elicitation gives a single necessary condition for consistency that applies to all of the above settings.
This criterion is implied by both consistency and calibration (as fully explored in Appendix \bo{TODO}), so it might be viewed as a weak necessary condition for existence of a dimension-$d$ surrogate.
Yet it gives state-of-the-art lower bounds on $d$.
In particular, indirect-elicitation bounds imply feasible subspace dimension bounds.

@@

\jessie{This section definitely needs some work because I'm not sure what is staying and what's going to the Appendix.}
\jessie{This proof uses calibration via Definition~\ref{def:calibrated-general}.}
\bo{Yeah, I skipped this since it seems like we won't bring in calibration definitions to the story...}
\begin{proposition}\label{prop:consistent-implies-calibrated}
	If a loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
	\jessiet{Probably appendix later; also, should this be a lemma instead of a proposition?}
%  \raft{Do we define ``continuous loss''?  Maybe ``(not necessarily discrete)'' is clearer.}
\end{proposition}
\begin{proof}
	We show the contrapositive.
	If $(L, \psi)$ are not calibrated with respect to $\ell$, then there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
	Suppose $D \sim \X \times\Y$ has only one $x \in \X$ with $Pr_D(X = x) > 0$ so that $p := D_x$ and $\E_D f(X,Y) = \E_p f(x, Y)$.
	Consider any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$.
  \raft{Type error with $D=D_x$; see AA15 for how they phrase \jessie{better?}}
	Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi \circ f(X), Y) \not \to \inf_f \E_D \ell(\psi \circ f(X), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$.
\end{proof}

\bo{Same here: appendix?}
\begin{lemma}\label{lem:calib-implies-indir}
	If a surrogate and link $(L, \psi)$ are calibrated with respect to a loss $\ell:\R \times\Y \to \reals$, then $L$ indirectly elicits the property $\gamma := \prop{\ell}$.
\end{lemma}
\begin{proof}
	Let $\Gamma$ be the unique property directly elicited by $L$, and fix $p \in \simplex$ with $u$ such that $p \in \Gamma_u$.
	As $p \in \Gamma_u$, then $\zeta(L(u;p) - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \risk{\ell}(p)$.
	We also have $\ell(\psi(u); p) \geq \risk{\ell}(p)$ by definition of $\risk{\ell}$, so we must have $\ell(\psi(u);p) = \risk{\ell}(p) = \ell(\gamma(p); p)$, and therefore, $p \in \gamma_{\psi(u)}$.
	Thus, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, so $L$ indirectly elicits $\gamma$.
\end{proof}

@@

\begin{definition}[Flat]
	A \emph{flat} $F \subseteq \affhull(\simplex) \subseteq \reals^n$ is a set $F = \ker W \cap \affhull(\simplex)$ for some $W\in\reals^{d\times n}$ where $d\leq n$.
	The codimension of $F$ (relative to $\affhull(\simplex)$) is given by $\codim(F)=\mathrm{rank}(W)$, and the dimension of $F$ is $n - \mathrm{rank}(W) - 1$.
\end{definition}

@@

	The $p$-weighted Minkowski sum $\oplus_y p_y \partial L(u,y) = \{p_1 x_1 + \ldots + p_n x_n : x_1 \in \partial L(u,1), \ldots, x_n \in \partial L(u,n) \}$.
	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, each choice of $x_i$ is a flat for $\partial L(u, i)$.
	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$; $W$ is similar to $\mathbf{A}^m$ in the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
	We can now take $F := \ker(W) \cap \affhull(\simplex)$, whose codimension relative to $\affhull(\simplex)$ is at most $d$.
	We particularly have $p \in \ker W$ by construction, and $p \in \simplex \implies p \in \affhull(\simplex)$, so we have $p \in F$.

	To see $F \cap \simplex \subseteq \gamma_r$, consider $q \in F \cap \simplex$.
	That would mean that $q \in F \implies \implies Wq = \vec 0 \implies \sum_y p_y x_y^i = 0$ for all $i \in [d]$, which in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u \subseteq \gamma_{r}$.
\end{proof}

Since Theorem~\ref{thm:consistent-implies-indir-elic} says that consistency implies indirect elicitation, we can now apply results on convex elicitation complexity, like the result above, to understand the minimal dimension required to construct a consistent surrogate loss.
Thus, elicitation complexity greater than $d$ implies no indirect elicitation of the property of interest (or target loss eliciting such a property), which in turn implies there is no $d$-dimensional consistent surrogate with respect to a given loss or property of interest.

@@

	As $L'$ is calibrated with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Theorem~\ref{thm:cvx-flats}, we know there exists a flat $F'$ of codimension $d$ relative to $\reals^{\Y'}$ so that $\dim(F') \geq \|p\|_0 - d - 1$.
	Moreover, as $d$ is the maximal codimension of such a flat, we show in Lemma~\ref{lem:feas-sub-is-a-flat} that $\S_{\gamma_r}(p)$ is one such flat, and we have $\dim(\S_{\gamma_r}(p)) \geq \dim(F') = \|p\|_0 - d- 1$.
	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\S_{\gamma'_r}(p)) = \dim(\S_{\gamma_r}(p))$, and from there we observe the result.
%	First, for intuition, consider $p \in \relint{\simplex}$. 
%	Theorem~\ref{thm:cvx-flats} implies that there exists a flat $F'$ of affine dimension at least $n-d-1$.
%	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\S_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\S_{\gamma_r}(p)) - 1$.
%
%	
%	If we can show that $L' := L|_{\Y'}$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then we observe the existence of a flat $F^*$ of codimension $d$ (in $\reals^{\Y'}$) so that $\dim(F^*) = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
%	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\S_{\gamma'_r}(p)) = \dim(\S_{\gamma_r}(p))$, and thus the result holds.
%	
%	Now to see that $L'$ is calibrated with respect to $\ell'$, consider that $\gamma(p) = \gamma'(p)$ for all $p \in \Delta^{\Y'}$,
%	\begin{align*}
%		\forall p \in \Delta_{\Y'}:  \inf_{u \in \reals^d : \psi(u) \not \in \gamma'(p)} L'(u;p) = \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p) = \inf_{u \in \reals^d} L'(u;p)~.~
%	\end{align*}
%	Therefore, we have $L'$ calibrated with respect to $\ell'$.
%
%	Moreover, we want to show $L'$ indirectly elicits $\gamma'$ so we can apply Theorem~\ref{thm:cvx-flats}.
%	First, observe that $L'$ elicits $\Gamma' : p \mapsto \Gamma(p)$ for all $p \in \Delta_{\Y'}$ 
%	For all $p \in \simplex$, we have $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$.
%	As $\Delta_{\Y'} \subseteq \simplex$, this is in particular true for all $p \in \Delta_{\Y'}$.
%	Therefore, for all $p \in \Delta_{\Y'}$, we have $\Gamma'_u = \Gamma_u \cap \Delta_{\Y'} \subseteq \gamma_{\psi(u)} \cap \Delta_{\Y'} = \gamma'_{\psi(u)}$, and thus $L'$ indirectly elicits $\gamma'$.
\end{proof}
\subsection{Example}\label{subsec:examples-finite}
There are some cases where the bound provided by Theorem~\ref{thm:cvx-flats} is strictly tighter than the bound provided by feasible subspace dimension in Corollary~\ref{cor:fsd-bound}.
For example, we can consider the \emph{abstain property} over 3 outcomes where one wishes to report the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and abstains from predicting ($\bot$) otherwise.
This is elicited by the target loss $\ell^{abs} := \mathbbm{1}\{r \not \in \{y, \bot\}\} + (1/2)\mathbbm{1}\{r = \bot\}$. 
We can consider two different distributions; in the first, our bound yields a strong gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
For this example, we choose $p$ to be the uniform distribution.
In this case, the bound by feasible subspace dimension yields $\ccdim(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
\raft{This is a bit of a strawman, since the FSD technique as a whole gives $\geq 1$ here, for e.g.\ $p=(1/4,1/4,1/2)$; let's maybe discuss both $p$'s for both techniques?}

@@

>>>>

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\simplex}{\Delta_\Y}
\newcommand{\relint}[1]{\mathrm{relint}(#1)}
\newcommand{\prop}[1]{\mathrm{prop}[#1]}
\newcommand{\elic}{\mathrm{elic}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
\newcommand{\ccdim}{\mathrm{cc\,dim}}
\newcommand{\codim}{\mathrm{codim}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\supp}{\mathrm{supp}}
\newcommand{\spn}{\mathrm{span}}
\newcommand{\propdis}{\mu}
\newcommand{\affhull}{\mathrm{affhull}}

@@

\subsection{Consistency and calibration for discrete convex losses}\label{subsec:convex-surrogates}

@@

\cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} form a characterization of consistent and calibrated surrogates for classification problems.
In finite prediction tasks, the two are in fact equivalent.  
\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, there is a consistent surrogate for binary classification problems, and~\cite{tewari2007consistency} generalizes this result for multiclass classification. 
\cite{ramaswamy2016convex} further show necessary and sufficient conditions for finite prediction problems to be consistent that can be applied to general discrete losses.
\cite{steinwart2007compare} generalizes the study of consistent losses from the finite prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration, giving proofs for various classes of surrogate losses (i.e. margin-based, distance-based, supervised, unsupervised, etc.)
See~\cite[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
In Appendix~\ref{app:calibration}, we give a more general definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in finite prediction settings, but generalizes to infinite prediction settings.

@@

\jessie{Mention calibration results are in the appendix if the reader wants that connection too.}
\paragraph{Our approach: indirect elicitation.}
In this section, we show that indirect elicitation gives a single necessary condition for consistency that applies to all of the above settings.
This criterion is implied by both consistency and calibration (as fully explored in Appendix \bo{TODO}), so it might be viewed as a weak necessary condition for existence of a dimension-$d$ surrogate.
Yet it gives state-of-the-art lower bounds on $d$.
In particular, indirect-elicitation bounds imply feasible subspace dimension bounds.

@@

@@

\begin{definition}[Flat]
	A \emph{flat} $F \subseteq \affhull(\simplex) \subseteq \reals^n$ is a nonempty set $F = \ker W \cap \affhull(\simplex)$ for some $W\in\reals^{d\times n}$ where $d\leq n$.
	The codimension of $F$ (relative to $\affhull(\simplex)$) is given by $\codim(F)=\mathrm{rank}(W)$, and the dimension of $F$ is $n - \mathrm{rank}(W) - 1$.
\end{definition}

@@

	The $p$-weighted Minkowski sum $\oplus_y p_y \partial L(u,y) = \{p_1 x_1 + \ldots + p_n x_n : x_1 \in \partial L(u,1), \ldots, x_n \in \partial L(u,n) \}$.
	In order for $\vec 0$ to be in this $p$-weighted Minkowski sum, each choice of $x_i$ is a flat for $\partial L(u, i)$.
	Moreover, with $p$ fixed, we know there is a vector of witnesses $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$ such that $\sum_y p_y x_y = \vec 0$.%; $W$ is similar to $\mathbf{A}^m$ in the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
	We can now take $F := \ker(W) \cap \affhull(\simplex)$, whose codimension relative to $\affhull(\simplex)$ is at most $d$.
	We particularly have $p \in \ker W$ by construction, and $p \in \simplex \implies p \in \affhull(\simplex)$, so we have $p \in F$.

	To see $F \cap \simplex \subseteq \gamma_r$, consider $q \in F \cap \simplex$.
	That would mean that $q \in F \implies Wq = \vec 0 \implies \sum_y p_y x_y^i = 0$ for all $i \in [d]$, which in turn implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u \subseteq \gamma_{r}$.
\end{proof}

\jessie{Discussion connecting to \cite{ramaswamy2016convex}.}
Since Theorem~\ref{thm:consistent-implies-indir-elic} says that consistency implies indirect elicitation, we can now apply results on convex elicitation complexity, like the result above, to understand the minimal dimension required to construct a consistent surrogate loss.
Thus, elicitation complexity greater than $d$ implies no indirect elicitation of the property of interest (or target loss eliciting such a property), which in turn implies there is no $d$-dimensional consistent surrogate with respect to a given loss or property of interest.

@@

	As $L'$ is calibrated with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Theorem~\ref{thm:cvx-flats}, we know there exists a flat $F' \subseteq$ of codimension $d$ relative to $\reals^{\Y'}$ so that $\codim(F') \leq d$.
	Moreover, as $d$ is the maximal codimension of such a flat, we show in Lemma~\ref{lem:feas-sub-is-a-flat} that $\S_{\gamma_r}(p)$ is one such flat, and we have $\dim(\S_{\gamma_r}(p)) \geq \dim(F') \geq \|p\|_0 - d- 1$.
	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\S_{\gamma'_r}(p)) = \dim(\S_{\gamma_r}(p))$, and from there we observe the result.
%	First, for intuition, consider $p \in \relint{\simplex}$. 
%	Theorem~\ref{thm:cvx-flats} implies that there exists a flat $F'$ of affine dimension at least $n-d-1$.
%	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\S_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\S_{\gamma_r}(p)) - 1$.
%
%	
%	If we can show that $L' := L|_{\Y'}$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then we observe the existence of a flat $F^*$ of codimension $d$ (in $\reals^{\Y'}$) so that $\dim(F^*) = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
%	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\S_{\gamma'_r}(p)) = \dim(\S_{\gamma_r}(p))$, and thus the result holds.
%	
%	Now to see that $L'$ is calibrated with respect to $\ell'$, consider that $\gamma(p) = \gamma'(p)$ for all $p \in \Delta^{\Y'}$,
%	\begin{align*}
%		\forall p \in \Delta_{\Y'}:  \inf_{u \in \reals^d : \psi(u) \not \in \gamma'(p)} L'(u;p) = \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p) = \inf_{u \in \reals^d} L'(u;p)~.~
%	\end{align*}
%	Therefore, we have $L'$ calibrated with respect to $\ell'$.
%
%	Moreover, we want to show $L'$ indirectly elicits $\gamma'$ so we can apply Theorem~\ref{thm:cvx-flats}.
%	First, observe that $L'$ elicits $\Gamma' : p \mapsto \Gamma(p)$ for all $p \in \Delta_{\Y'}$ 
%	For all $p \in \simplex$, we have $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$.
%	As $\Delta_{\Y'} \subseteq \simplex$, this is in particular true for all $p \in \Delta_{\Y'}$.
%	Therefore, for all $p \in \Delta_{\Y'}$, we have $\Gamma'_u = \Gamma_u \cap \Delta_{\Y'} \subseteq \gamma_{\psi(u)} \cap \Delta_{\Y'} = \gamma'_{\psi(u)}$, and thus $L'$ indirectly elicits $\gamma'$.
\end{proof}
\subsection{Example}\label{subsec:examples-finite}
There are some cases where the bound provided by Theorem~\ref{thm:cvx-flats} is strictly tighter than the bound provided by feasible subspace dimension in Corollary~\ref{cor:fsd-bound}.
For example, we can consider the \emph{abstain property} over 3 outcomes where one wishes to report the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and abstains from predicting ($\bot$) otherwise.
This is elicited by the target loss $\ell^{abs}(r,y) := \mathbbm{1}\{r \not \in \{y, \bot\}\} + (1/2)\mathbbm{1}\{r = \bot\}$. 
We can consider two different distributions; in the first, our bound yields a strong gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
For this example, we choose $p$ to be the uniform distribution.
In this case, the bound by feasible subspace dimension yields $\ccdim(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
\raft{This is a bit of a strawman, since the FSD technique as a whole gives $\geq 1$ here, for e.g.\ $p=(1/4,1/4,1/2)$; let's maybe discuss both $p$'s for both techniques?}

@@

\subsection{Relating calibration, consistency, and indirect elicitation.}
Even with the more general notion of calibration that extends beyond discrete predictions, we still have consistency implying calibration.
\begin{proposition}\label{prop:consistent-implies-calibrated}
	If a loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
	\jessiet{Probably appendix later; also, should this be a lemma instead of a proposition?}
	%  \raft{Do we define ``continuous loss''?  Maybe ``(not necessarily discrete)'' is clearer.}
\end{proposition}
\begin{proof}
	We show the contrapositive.
	If $(L, \psi)$ are not calibrated with respect to $\ell$, then there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
	Suppose $D \sim \X \times\Y$ has only one $x \in \X$ with $Pr_D(X = x) > 0$ so that $p := D_x$ and $\E_D f(X,Y) = \E_p f(x, Y)$.
	Consider any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$.
	\raft{Type error with $D=D_x$; see AA15 for how they phrase \jessie{better?}}
	Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi \circ f(X), Y) \not \to \inf_f \E_D \ell(\psi \circ f(X), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$.
\end{proof}

Moreover, we have calibration implying indirect elicitation.
\begin{lemma}\label{lem:calib-implies-indir}
	If a surrogate and link $(L, \psi)$ are calibrated with respect to a loss $\ell:\R \times\Y \to \reals$, then $L$ indirectly elicits the property $\gamma := \prop{\ell}$.
\end{lemma}
\begin{proof}
	Let $\Gamma$ be the unique property directly elicited by $L$, and fix $p \in \simplex$ with $u$ such that $p \in \Gamma_u$.
	As $p \in \Gamma_u$, then $\zeta(L(u;p) - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \risk{\ell}(p)$.
	We also have $\ell(\psi(u); p) \geq \risk{\ell}(p)$ by definition of $\risk{\ell}$, so we must have $\ell(\psi(u);p) = \risk{\ell}(p) = \ell(\gamma(p); p)$, and therefore, $p \in \gamma_{\psi(u)}$.
	Thus, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, so $L$ indirectly elicits $\gamma$.
\end{proof}

Combining the two results, we can observe the result of Theorem~\ref{thm:consistent-implies-indir-elic} another way: \emph{through calibration}.
